PCA on Finnish Municipalities

### 2022-04-07 MSA-Project.Rmd
Updated report

subtitle: "Dimensionality reduction with PCA on Finnish municipalities' demographic variables"
geometry: top=0.7in, bottom=0.5in, left=0.5in, right=0.7in
---

>>>>

subtitle: "Dimensionality reduction with PCA on Finnish municipality demographics"
geometry: top=0.7in, bottom=0.5in, left=0.5in, right=0.7in
---
